Super awesome embeddings

### 2019-02-03 paper/main.tex

\section{Experiments}
\subsection{Assumptions}
Since our goal is to check how embedding approach works for WSD problem, we use pretrained embedding model from spaCy - en\_vectors\_web\_lg.
Due to high impact of training data order on test results, as a result we take average score of 30 runs for each optimization with random order of training data. The best configuration of each experiment is taken as a baseline for the next experiment.
The goal of these experiments is to show how each of parameters influences on model's accuracy after training.
\subsection{Baseline}
First of experiments is to check how out-of-the-box model works without extra optimizations. We perform tests with different context lengths, as a score we choose top 1 and top 3 accuracy. Results are shown in the Fig. \ref{fig:baseline}.

@@

We see that the base model exceeds 90 percentages of top 3 accuracy for very short context length. It may be caused by low number of meanings of each disambiguation word.
We also see that top 1 score is the best for context length of 3 and we will use it in next two experiments as a baseline.

\subsection{Context length optimization}
Once we have base model results we check how simple alpha optimization improves accuracy based on context length. To do this, we choose arbitrarily a value for alpha parameter and run tests after one epoch of training the model. Since we average results from 30 runs we mark the measurement uncertainty on the graph. Results are shown in the Fig. \ref{fig:exp1}.
\begin{figure}
    \label{fig:exp1}
    \caption{Comparison of the base model and a little bit optimized model based on different context length}
    \includegraphics[scale=0.6]{res/exp1_context_top_acc.png}
\end{figure}
Independent on some noise caused by random order of training data, the optimized model is much better than the base model. Another fact is that for tested alpha parameter, longer context gives better results than with context's length obtained in the previous experiment.

@@

We observe that optimal value of alpha is 0.25 but higher values may cause worse accuracy score than the baseline. As alpha is responsible for reducing distance between context and keyword (Equation \ref{eq:alpha_optimization}) and it is a scalar value, it may move the keyword to the other side and in the result the distance may be increased. It is one of things that can be improved in future work.

>>>>

\section{Experiments}
\subsection{Assumptions}
Since our goal is to check how embedding approach works for WSD problem, we use pretrained embedding model from spaCy - en\_vectors\_web\_lg, 300-dimensional word vectors trained on Common Crawl with GloVe.\cite{spacymodel}.
Due to high impact of training data order on test results, we take the average score of 30 runs (with random order of training data) for each optimization experiment.
The best configuration of each experiment is taken as a baseline for the next experiment.
The goal of these experiments is to show how each of parameters influences on model's accuracy after training.
\subsection{Baseline}
First of experiments is to check how out-of-the-box model works without extra optimizations. We perform tests with different context lengths, as a score we choose top 1 and top 3 accuracy. Results are shown in the Fig. \ref{fig:baseline}.

@@

We see that the base model exceeds 90 percentages of top 3 accuracy for very short context length. It may be caused by low number of meanings of each disambiguation word.
It can also be observed that top 1 score is the best for context length of 3 and therefore we decided to use it as a baseline for next two experiments.

\subsection{Context length optimization}
Once we have base model results we check how simple alpha optimization improves accuracy based on context length. To do this, we choose arbitrarily a value for alpha parameter and run tests after one epoch of training the model. Since we average results from 30 runs we mark the measurement uncertainty on the graph. Results are shown in the Fig. \ref{fig:exp1}.
\begin{figure}
    \label{fig:exp1}
    \caption{Comparison of the base model and a little bit optimized model based on different context length}
    \includegraphics[scale=0.6]{res/exp1_context_top_acc.png}
\end{figure}
Independent of some noise caused by random order of training data, the optimized model is much better than the base model. Interestingly, the improvement is most visible for long context lengths, which achieved relatively poor results in the baseline experiment.

@@

We observe that optimal value of alpha is 0.25 but higher values may cause worse accuracy score than the baseline. As alpha is responsible for reducing distance between context and keyword (Equation \ref{eq:alpha_optimization}) and it is a scalar value, it moves the keyword closer to correct context but after moving, the keyword may be also closer to the other, incorrect context.
